quollr: An R Package for Visualizing $2-D$ Models from Non-linear Dimension Reductions in High Dimensional Space

### 2024-06-22 paper-quollr.Rmd
Add section prediction

@@

>>>>

The `predict_emb()` function is used to predict $2\text{-}D$ embedding for a new $p\text{-}D$ data point using the fitted model. This function is useful to predict $2\text{-}D$ embedding irrespective of the NLDR technique.

In the prediction process, first, the nearest $p\text{-}D$ model point is identified for a given new $p\text{-}D$ point by computing $p\text{-}D$ Euclidean distance. Then, the corresponding $2-D$ bin centroid mapping for the identified $p\text{-}D$ model point is determined. Finally, the coordinates of the identified $2\text{-}D$ bin centroid is used as the predicted NLDR point for the new $p\text{-}D$ data point.

```{r, echo=TRUE, eval=FALSE}
predict_emb(
  test_data = s_curve_noise_training, 
  df_bin_centroids = df_bin_centroids, 
  df_bin = df_bin, 
  type_NLDR = "UMAP"
  )
```

@@

As a Goodness of fit statistics for the model, `glance()` is used to compute residuals and MSE. These metrics are used to assess how well the fitted model will capture the underlying structure of the $p\text{-}D$ data.

```{r, echo=TRUE, eval=FALSE}
glance(
  df_bin_centroids = df_bin_centroids, 
  df_bin = df_bin, 
  training_data = s_curve_noise_training, 
  newdata = NULL, 
  type_NLDR = "UMAP", 
  col_start = "x"
  )
```

```{r, echo=TRUE, eval=FALSE}
augment(
  df_bin_centroids = df_bin_centroids, 
  df_bin = df_bin, 
  training_data = s_curve_noise_training, 
  newdata = NULL, 
  type_NLDR = "UMAP", 
  col_start = "x"
  )
```
